### 2021-06-10 paper/appendix_data.tex
Cleaned up comments, added sentence on model for recorded cases.

\subsection{Number of Contacts}
\label{sub:number_of_contacts}

@@

\subsection{Infection Probabilities}
\label{subsec:infection_probs}

@@

Currently, we use data for Germany from October 2020 until June 2021. We do not use
earlier periods for three reasons. Firstly, in the beginning PCR tests were highly
limited and therefore it would be difficult to find good initial conditions for our
simulations. In addition during the summer the case numbers were extremely low. This
could lead to the epidemic going extinct in our simulation. Additionally, our model does
not include international travel or other imports of cases. These would be important but
difficult to model during the summer months.

@@

The infection probabilities estimated from our model are as follows: For household
contacts (each individual meets all his or her household members every day) the infection
probability is 10\%, for school contacts (all students and teachers meet all other
students and teachers that attend school that day and there are three classes taking
place each day) the probability of infection is 1.2\%, for preschools and nurseries that
infection probability is 0.5\%. Work contacts carry a risk of 14.5\% and other activities
(including leisure activities such as meeting friends) carry the highest risk with
15.875\%.

>>>>

\subsection{Number of Contacts\comment[id=HM]{Histograms seem like the way to go here. Also add household contacts, i.e., distribution of (household size minus 1).}}
\label{sub:number_of_contacts}

@@

\subsection{Infection Probabilities\comment[id=HM]{Is the data section the right place?}}
\label{subsec:infection_probs}

@@

We use data for Germany from October 2020 until June 2021. We do not use
earlier periods for three reasons. Firstly, in the beginning PCR tests were highly
limited and therefore it would be difficult to find good initial conditions for our
simulations. In addition during the summer the case numbers were extremely low. This
could lead to the epidemic going extinct in our simulation. Additionally, our model does
not include international travel or other imports of cases. These would be important but
difficult to model during the summer months.

@@

The infection probabilities estimated from our model are as follows: For household
contacts (each individual meets all his or her household members every day) the infection
probability is 10\%, for school contacts (all students and teachers meet all other
students and teachers that attend school that day and there are three classes taking
place each day) the probability of infection is 1.2\%, for preschools and nurseries that
infection probability is 0.5\%. Work contacts carry a risk of 14.5\% and other activities
(including leisure activities such as meeting friends) carry the highest risk with
15.875\%.\comment[id=HM]{Are these numbers current? In any case, a table would substitute for this and the previous paragraph. Need to mention B.1.1.7 alongside.}

### 2021-06-10 paper/report.tex
Improve on the policies section by adding multiplier plots and adding seasonality to the policy discussion.
Cleaned up comments, added sentence on model for recorded cases.

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=K]{WHO Press Conference saying we won't reach herd
immunity in 2021. She cites no source.}\comment[id=HM]{If we find a paper (s)he cites, would be even better}
In the meantime, it is of utmost importance to employ an effective mix of strategies for
containing the virus. The most frequent initial response was a set of non-pharmaceutical
interventions (NPIs) to reduce contacts between individuals. While this has allowed some
countries to sustain equilibria with very low infection numbers\footnote{See
    \citet{Contreras2021} for a theoretical equilibrium at low case numbers which is
    sustained with test-trace-and-isolate policies.}, most have seen large fluctuations of
infection rates. Containment measures have become increasingly diverse and now include
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or more infectious virus strains are well understood in
quantitative terms.

@@

        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-left}
        \caption{{Model for antigen tests}}
        \label{fig:antigen_tests}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-right}
        \caption{{Model for undetected cases}}
        \label{fig:model_for_official_cases}
    \end{subfigure}

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for an overview.} We can rely on contact diaries to get pre-pandemic
distributions of contacts for different contact types and their assortativity by age
group. Mobility data is used to model the reductions in work contacts. School and daycare
policies can be incorporated directly from official directives. Aggregate tests,
vaccinations and the prevalence of virus strains can be taken from official records. The
likelihood to receive a test offer or to take up a test offer and the share of
individuals that have ever taken a test or done weekly tests in the last month can be
calibrated from survey data.\comment[id=HM]{Anything else we need to
mention?}\comment[id=K]{I added some more that I think are worth mentioning.} We estimate
the infection probabilities\comment[id=HM]{need to be more precise here, cannot find in
Appendix}\comment[id=K]{I added \ref{subsec:infection_probs}.} that the simulated new
infections predict age- and region-specific time series.\comment[id=K]{We never directly
targeted the federal states if I remember it right. How large was their weight in the
criterion function @Janos?} However, the two sets of time series are not comparable
directly because not all cases will be recorded. We model the fraction of recorded cases
as depicted in Figure~\ref{fig:model_for_official_cases}.\comment[id=HM]{Add a sentence.}

@@

Effects:
\begin{itemize}
    \item Schools were essentially closed
    \item What are the different $R_t$-values? In no-test scenario and $R_t>1$, might be
          worth chopping off 0.05 or whatever that might be?
    \item With tests it is really hard to make a case for that
\end{itemize}

>>>>

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=HM]{Need to find some more scientific citation
before submission} In the meantime, it is of utmost importance to employ an effective
mix of strategies for containing the virus. The most frequent initial response was a set
of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While
this has allowed some countries to sustain equilibria with very low infection
numbers\footnote{See \citet{Contreras2021} for a theoretical equilibrium at low case
    numbers which is sustained with test-trace-and-isolate policies.}, most have seen large
fluctuations of infection rates. Containment measures have become increasingly diverse
and now include testing, more nuanced NPIs, and contact tracing. Neither these policies'
effect nor the influence of seasonal patterns or more infectious virus strains are well
understood in quantitative terms.

@@

        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-left}
        \caption{{Model for antigen tests}}
        \label{fig:antigen_tests}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.425\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/model-graph-bottom-right}
        \caption{{Translating all infections to recorded ones}}
        \label{fig:model_for_official_cases}
    \end{subfigure}

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
    materials for an overview.} Contact diaries yield pre-pandemic distributions of contacts
for different contact types and their assortativity by age group. Mobility data is used
to model the reductions in work contacts. School and daycare policies can be
incorporated directly from official directives. Administrative records on the number of
tests, vaccinations by age and region, and the prevalence of virus strains are generally
available. Surveys may ask about test offers, propensities to take them up, and past
tests.

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that  simulated
infections by age predict the corresponding time series in the data \citep[See][for the
    general method]{McFadden1989}. However, the two sets of time series are not comparable
directly because not all cases will be recorded. We thus model recorded cases as
depicted in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of
the share of recorded cases and use data on whether the reason for a PCR test were
symptoms of CoViD-19 to get age-specific shares. For example,
\comment[id=HM]{@Janos, please correct if necessary and insert reference} estimate
unknown cases to be twice as high for children as for adults. Confirmation of a positive
rapid test result is another reason for PCR tests, once these become available.

@@
